---
title: "Analysis"
author: "Adama NDOUR"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load package
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(paletteer)
library(meta) # meta-analysis
library(nnet) # Multinomial logit model
library(GGally) # plot model coefficients
library(report) # report statistical results
library(stargazer) # formatting statistical results
library(kableExtra) # format table
library(DHARMa) # plot residuals of a linear model
```


## Load the data
```{r}
df <- read_excel("uav_review_data.xlsx")
```

## Overview of the data
```{r}
#str(df)
```

## Data manipulation: create a model class variable
```{r}
df <- df %>% mutate(
  Model_Class = case_when(
    RPD < 1.4 ~ "unrealiable models",
    RPD >= 1.4 & RPD < 2 ~ "reasonable models",
    RPD >=2 ~ "excellent models"
  )
)

# Remove special characters
df$Sensor <- str_replace_all(df$Sensor, "\r", " ")
df$Sensor <- str_replace_all(df$Sensor, "\n", " ")
df$Sensor <- str_replace_all(df$Sensor, "\\s+", " ")
```

## Exploratory Data Analysis (EDA)

### Typology of Algorithms
```{r}
library(treemap)
library(ggplotify)
t <- df %>% 
  count(Algorithm)
algos <- t %>% mutate(tot = sum(n)) %>% mutate(perc = (n/tot)*100)
algos$label <- paste0(algos$n, " %")
algos$label_comp <- paste(algos$Algorithm, algos$label, sep = "\n")
# Open a PNG device
#png("output/treemap_algos_2.png", width = 8, height = 6, units = "in",res = 300)
treemap(
  algos,
  index = "Algorithm",
  vSize = "perc",
  title = "",
  fontsize.labels = 12,
  #fontcolor.labels = "white",
)
#dev.off()
```

### Which UAV platform maximize the performance of ML models
```{r fig.height=5, fig.width=7, message=FALSE, warning=FALSE, dpi=300}
df_trait <- df %>% filter(Problem=="trait estimation")
#df_trait %>% group_by(Crop,Algorithm)
n_shape_var <- length(unique(df_trait$Sensor))
df_trait_sum <- df_trait %>% 
  group_by(DOI, Trait, UAV_Type, Sensor, Algorithm,Model_Class) %>% 
  summarise(RPD=mean(RPD))
p<- df_trait_sum %>% 
  ggplot(aes(y=Algorithm, x=RPD, color=UAV_Type)) +
  geom_point(aes(shape=Sensor))+
  scale_shape_manual(values = 0:n_shape_var) +
  scale_color_paletteer_d("ggthemes::calc")+
  facet_grid(Trait~ Model_Class, scales = "free_y")+
  theme_bw()+
  theme(
    legend.text = element_text(size = 8.5)
  )+
  geom_vline(xintercept = c(1.4, 2), 
             linetype = "dashed", color = "black", size=0.3 )
  
ggsave("output/figure1.png",plot = p,dpi = 300)
p
```


### Forest plot for the biomass

```{r fig.height=5, fig.width=10, message=FALSE, warning=FALSE, dpi=300}
# Install and load necessary packages
# Load necessary libraries

# Example RPD data
biomass_data <- df_trait %>% filter(Trait=="AGB")

# Calculate summary statistics
biomass_rpd_summary <- biomass_data %>%
  group_by(Algorithm) %>%
  summarize(
    mean_RPD = mean(RPD),
    sd_RPD = sd(RPD),
    n = n(),
    SEM_RPD = sd_RPD / sqrt(n),
    CI_Lower = mean_RPD - 1.96 * SEM_RPD,
    CI_Upper = mean_RPD + 1.96 * SEM_RPD
  )

# Print the summary
print(biomass_rpd_summary)

# Combine data for all models
biomass_meta_combined <- metagen(
  TE = biomass_rpd_summary$mean_RPD,
  lower = biomass_rpd_summary$CI_Lower,
  upper = biomass_rpd_summary$CI_Upper,
  studlab = biomass_rpd_summary$Algorithm,
  sm = "Mean"
)

# Forest plot for all models
png(file = "output/forestplot_biomass.png", width = 10, height = 5, res = 300, units = "in")
forest(biomass_meta_combined,
       main = "Forest Plot of RPD for All Models of Biomass Estimation",
       xlab = "RPD",
       studlab = biomass_rpd_summary$Algorithm,
       print.tau2 = FALSE,
       col.diamond = "blue",
       col.predict = "red",
       rightcols = c("effect", "ci","w.common"),
       leftcols = c("studlab"),
       leftlabs = c("Models"))



```


### Forest plot for the yield

```{r fig.height=5, fig.width=10, message=FALSE, warning=FALSE, dpi=300}
# Install and load necessary packages
# Load necessary libraries

# Example RPD data
yield_data <- df_trait %>% filter(Trait=="Yield")

# Calculate summary statistics
yield_rpd_summary <- yield_data %>%
  group_by(Algorithm) %>%
  summarize(
    mean_RPD = mean(RPD),
    sd_RPD = sd(RPD),
    n = n(),
    SEM_RPD = sd_RPD / sqrt(n),
    CI_Lower = mean_RPD - 1.96 * SEM_RPD,
    CI_Upper = mean_RPD + 1.96 * SEM_RPD
  )

# Print the summary
print(yield_rpd_summary)

# Combine data for all models
yield_meta_combined <- metagen(
  TE = yield_rpd_summary$mean_RPD,
  lower = yield_rpd_summary$CI_Lower,
  upper = yield_rpd_summary$CI_Upper,
  studlab = yield_rpd_summary$Algorithm,
  sm = "Mean"
)

# Forest plot for all models
png(file = "output/forestplot_yield.png", width = 10, height = 5, res = 300, units = "in")
forest(yield_meta_combined,
       main = "Forest Plot of RPD for All Models for Yield Estimation",
       xlab = "RPD",
       label.left = "Models",
       studlab = yield_rpd_summary$Algorithm,
       print.tau2 = FALSE,
       col.diamond = "blue",
       col.predict = "red",
       rightcols = c("effect", "ci","w.common"),
       leftcols = c("studlab"),
       leftlabs = c("Models"),
       layout = "meta"
       
       )
dev.off()
```

### Forest plot for the nitrogen

```{r fig.height=5, fig.width=10, message=FALSE, warning=FALSE, dpi=300}
# Install and load necessary packages
# Load necessary libraries
library(meta)

# Example RPD data
nitrogen_data <- df_trait %>% filter(Trait=="Nitrogen")

# Calculate summary statistics
nitrogen_rpd_summary <- nitrogen_data %>%
  group_by(Algorithm) %>%
  summarize(
    mean_RPD = mean(RPD),
    sd_RPD = sd(RPD),
    n = n(),
    SEM_RPD = sd_RPD / sqrt(n),
    CI_Lower = mean_RPD - 1.96 * SEM_RPD,
    CI_Upper = mean_RPD + 1.96 * SEM_RPD
  )

# Print the summary
print(nitrogen_rpd_summary)

# Combine data for all models
nitrogen_meta_combined <- metagen(
  TE = nitrogen_rpd_summary$mean_RPD,
  lower = nitrogen_rpd_summary$CI_Lower,
  upper = nitrogen_rpd_summary$CI_Upper,
  studlab = nitrogen_rpd_summary$Algorithm,
  sm = "Mean"
)

# Forest plot for all models
png(file = "output/forestplot_nitrogen.png", width = 10, height = 5, res = 300, units = "in")
forest(nitrogen_meta_combined,
       main = "Forest Plot of RPD for All Models of nitrogen Estimation",
       xlab = "RPD",
       label.left = "Models",
       studlab = nitrogen_rpd_summary$Algorithm,
       print.tau2 = FALSE,
       comb.random = FALSE,
       col.diamond = "blue",
       col.predict = "red",
       rightcols = c("effect", "ci","w.common"),
       leftcols = c("studlab"),
       leftlabs = c("Models"),
       layout = "meta")

```

## Multivariate Linear Regression: Key drivers of ML model performance 
```{r}
# Recode RPD variable to convert to factor predictors
# df_trait_model <- df_trait %>% 
#   mutate(
#     RPD_rec = recode_factor(Model_Class, 
#                             "unrealiable models" = "Bad",
#                             "reasonable models" = "Reliable",
#                             "excellent models" = "Excellent"),
#     Crop = as_factor(Crop),
#     Stage = as_factor(Stage),
#     Trait = as_factor(Trait),
#     UAV_Type = as_factor(UAV_Type),
#     Sensor = as_factor(Sensor),
#     Band = as_factor(Band),
#     Algorithm = as_factor(Algorithm)
#   )
df_trait_model <- df_trait %>% 
  select(RPD, DOI, Crop, Stage, Trait, UAV_Type, Sensor, Band, Altitude_m, Algorithm)

```


```{r}
# Drop Na
df_trait_model <- df_trait_model %>% drop_na(UAV_Type)
# Data manipulation
df_trait_model$Band <- str_replace_all(df_trait_model$Band,", ","_")

```



```{r}
library(forcats)
# Group sensor levels
df_trait_model_rec1 <- df_trait_model %>% 
  # group_by(Sensor) %>% 
  # filter(n_distinct(DOI) >= 2) %>% 
  # ungroup()
  mutate(Sensor = case_when(
    grepl("^Micasense RedEdge",Sensor)~ "Micasense RedEdge",
    grepl("^Parrot Sequoia", Sensor) ~ "Parrot Sequoia",
    TRUE ~ "Other"
  ))

# Remove crops that appear in one paper and group cereal crops
df_trait_model_rec2<- df_trait_model_rec1 %>%
  # group_by(Crop) %>%
  # filter(n_distinct(DOI) >= 2) #%>%
  # ungroup() %>%
  mutate(
    Crop = case_when(
      (Crop=="maize") | (Crop=="rice") | Crop=="wheat" ~ "cereal",
      TRUE~Crop
    )
  )

# Group DJI matrice UAVs and remove UAVs that appear in one paper
df_trait_model_rec3 <- df_trait_model_rec2 %>%
  mutate(UAV_Type = case_when(
    grepl("^DJI Matrice", UAV_Type) ~ "DJI Matrice",
    TRUE ~ UAV_Type
  )) 
#   group_by(UAV_Type) %>% 
#   filter(n_distinct(DOI) >= 2) %>% 
#   ungroup() 

# Remove bands that appear in one paper
# df_trait_model_rec3 <- df_trait_model_rec2 %>% 
#   group_by(Band) %>% 
#   filter(n_distinct(DOI) >= 2) %>% 
#   ungroup()

# Remove algorithms that appear in one paper
df_trait_model_rec4 <- df_trait_model_rec3 %>% 
  mutate(across(where(is.character), ~ as.factor(.x))) %>% 
  # group_by(Algorithm) %>% 
  # filter(n_distinct(DOI) >= 2) %>% 
  # ungroup() 
  mutate(Algorithm = fct_lump(Algorithm,4))

# Select the final variables for the regression analysis

df_trait_model_rec5 <- df_trait_model_rec4 %>% 
  # mutate(across(where(is.character), ~ as.factor(.x))) %>% 
  # mutate(across(where(is.factor), ~ fct_lump(.x, 3))) %>% 
  select(RPD, Trait,Crop, UAV_Type, Sensor, Band, Algorithm, Altitude_m)
```


## Modeling
```{r}
model_data <- df_trait_model_rec5
write.csv(model_data,file = "output/model_data.csv",row.names = F)
```

### Check collinearity between features
```{r}
library(fastDummies)
check_corr <- function(trait_data) {
  dummy_data <- dummy_cols(trait_data, 
                           select_columns = c("Crop", "UAV_Type", 
                                              "Sensor", "Band", "Algorithm"),
                           remove_first_dummy = F,  # Optionally remove the first                             dummy to avoid multicollinearity
                          remove_selected_columns = TRUE)  # Remove original columns
  
  corr_matrix <- cor(dummy_data)
  corrplot::corrplot(corr = corr_matrix)
  return (dummy_data)}


```


### biomass
```{r}
biomass_data <- model_data %>% 
  filter(Trait=="AGB") %>% 
  select(-Trait)
```
#### Definition of the intercept
Let set the intercept to be Crop = cereal, UAV Type = AscTec Pelican, Sensor = Micasense RedEdge, Band = B_G_R_RE_NIR, Algorithm = MLR, and Altitude = 15:
```{r}
# Relevel categorical variables
biomass_data$Crop <- relevel(biomass_data$Crop, ref = "cereal")
biomass_data$Crop <- droplevels(biomass_data$Crop) # drop levels that doesn't exist
biomass_data$UAV_Type <- relevel(biomass_data$UAV_Type, ref = "eBee wing-fixed")
biomass_data$UAV_Type <- droplevels(biomass_data$UAV_Type)
biomass_data$Sensor <- relevel(biomass_data$Sensor, ref = "Micasense RedEdge")
biomass_data$Sensor <- droplevels(biomass_data$Sensor)
biomass_data$Band <- relevel(biomass_data$Band, ref = "B_G_R_RE_NIR")
biomass_data$Band <- droplevels(biomass_data$Band)
biomass_data$Algorithm <- relevel(biomass_data$Algorithm, ref = "MLR")
biomass_data$Algorithm <- droplevels(biomass_data$Algorithm)

# Set altitude to 15 as a reference: subtract 15 from all the values in the Altitude column. This will make 15 the reference point (i.e., the value where Altitude = 0 in the model).
#biomass_data$Altitude_m <- biomass_data$Altitude_m
```

#### Preprocess the data
```{r}
biomass_data_final <- check_corr(biomass_data)
```

#### Model Building


```{r}
library(glmnet)

# Prepare the data
y <- biomass_data_final$RPD
X <- select(biomass_data_final, -c(RPD, Altitude_m))  # Exclude intercept
X <- as.matrix(X)
X_interactions <- model.matrix(~ (.)^2, data = as.data.frame(X))
X_interactions <- X_interactions[,-1] # remove intercept

# Perform cross-validation to find the best alpha and lambda
set.seed(123)  # For reproducibility
cv_elastic_net <- cv.glmnet(X_interactions, y, alpha = 0.5)  # alpha = 0.5 for Elastic Net

# Extract the best lambda value
best_lambda <- cv_elastic_net$lambda.min

# Fit the final Elastic Net model
final_model <- glmnet(X_interactions, y, alpha = 0.5, lambda = best_lambda)

# View the coefficients
#print(coef(final_model))
```

#### Plot interactions
```{r fig.height=8, fig.width=18, warning=FALSE, fig.dpi=300}
library(networkD3)
library(ggraph)
library(tidygraph)
library(tidyr)
library(dplyr)
set_graph_style(plot_margin = margin(1,1,1,1))

# Get the coefficients of the variables
coefficients <- coef(final_model)
df_coefs <- data.frame(
     variables = names(coefficients[,1]),
     coef_estimates = as.numeric(coefficients[,1])
 )

# Remove zero coefficients
df_coefs <- df_coefs %>% filter(coef_estimates !=0)


# Split variables string in 2 columns using the ':' as the separator
df_coefs2 <- df_coefs %>%
  separate(variables, into = c("Var1", "Var2"), sep = ":")  # Separate the interaction terms
write.csv(df_coefs2, file="output/biomass_elasticnet_results.csv", row.names = F)

interaction_df <-df_coefs2 %>% filter(!is.na(Var2))

nodes <- unique(c(interaction_df$Var1, interaction_df$Var2))
edges <- data.frame(
  from = match(interaction_df$Var1, nodes),
  to = match(interaction_df$Var2, nodes) ,
  value = abs(interaction_df$coef_estimates)*5
) %>% 
  mutate(contribution = ifelse(interaction_df$coef_estimates>0, "positive", "negative"))
nods <- data.frame(name=nodes)
graph <- tbl_graph(nodes=nods, edges=edges, directed = F)


# Not specifying the layout - defaults to "auto"

p<-ggraph(graph, layout = 'stress') + 
  geom_edge_link(aes(colour=contribution)) +
  geom_node_point(size=7, color="blue", alpha=0.6)+
  geom_node_text(aes(label = name), vjust = 1.5, size=5.5)+
  theme_graph(base_size = 18)+
  theme(legend.position = "top")
p

# Save the graph 
ggsave("output/interaction_network_biomass.png", p, units = "in",
       width = 18, height = 8, dpi = 300)


```



<!-- #### Plot the residuals -->
<!-- ```{r message=FALSE, warning=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE, dpi=300} -->
<!-- simulationOutput <- simulateResiduals(fittedModel = final_model) -->
<!-- plot(simulationOutput) -->

<!-- ``` -->

### Yield
```{r}
yield_data <- model_data %>% 
  filter(Trait=="Yield") %>% 
  select(-Trait)
```
#### Definition of the intercept
Let set the intercept to be Crop = cereal, UAV Type = AscTec Pelican, Sensor = Micasense RedEdge, Band = B_G_R_RE_NIR, Algorithm = MLR, and Altitude = 15:
```{r}
# Relevel categorical variables
yield_data$Crop <- relevel(yield_data$Crop, ref = "cereal")
yield_data$Crop <- droplevels(yield_data$Crop) # drop levels that doesn't exist
yield_data$UAV_Type <- relevel(yield_data$UAV_Type, ref = "eBee wing-fixed")
yield_data$UAV_Type <- droplevels(yield_data$UAV_Type)
yield_data$Sensor <- relevel(yield_data$Sensor, ref = "Micasense RedEdge")
yield_data$Sensor <- droplevels(yield_data$Sensor)
yield_data$Band <- relevel(yield_data$Band, ref = "B_G_R_RE_NIR")
yield_data$Band <- droplevels(yield_data$Band)
yield_data$Algorithm <- relevel(yield_data$Algorithm, ref = "MLR")
yield_data$Algorithm <- droplevels(yield_data$Algorithm)

# Set altitude to 15 as a reference: subtract 15 from all the values in the Altitude column. This will make 15 the reference point (i.e., the value where Altitude = 0 in the model).
#yield_data$Altitude_m <- yield_data$Altitude_m
```

#### Preprocess the data
```{r}
yield_data_final <- check_corr(yield_data)
```

#### Model Building


```{r}
library(glmnet)

# Prepare the data
y <- yield_data_final$RPD
X <- select(yield_data_final, -c(RPD))  #-c(RPD, Altitude_m)
X <- as.matrix(X)
X_interactions <- model.matrix(~ (.)^2, data = as.data.frame(X))
X_interactions <- X_interactions[,-1] # remove intercept

# Perform cross-validation to find the best alpha and lambda
set.seed(123)  # For reproducibility
cv_elastic_net <- cv.glmnet(X_interactions, y, alpha = 0.5)  # alpha = 0.5 for Elastic Net

# Extract the best lambda value
best_lambda <- cv_elastic_net$lambda.min

# Fit the final Elastic Net model
final_model <- glmnet(X_interactions, y, alpha = 0.5, lambda = best_lambda)

# View the coefficients
#print(coef(final_model))
```

#### Plot interactions
```{r fig.height=8, fig.width=18, warning=FALSE, fig.dpi=300}
library(networkD3)
library(ggraph)
library(tidygraph)
library(tidyr)
library(dplyr)
set_graph_style(plot_margin = margin(1,1,1,1))

# Get the coefficients of the variables
coefficients <- coef(final_model)
df_coefs <- data.frame(
     variables = names(coefficients[,1]),
     coef_estimates = as.numeric(coefficients[,1])
 )

# Remove zero coefficients
df_coefs <- df_coefs %>% filter(coef_estimates !=0)


# Split variables string in 2 columns using the ':' as the separator
df_coefs2 <- df_coefs %>%
  separate(variables, into = c("Var1", "Var2"), sep = ":")  # Separate the interaction terms

write.csv(df_coefs2, file="output/yield_elasticnet_results.csv", row.names = F)

interaction_df <-df_coefs2 %>% filter(!is.na(Var2))

nodes <- unique(c(interaction_df$Var1, interaction_df$Var2))
edges <- data.frame(
  from = match(interaction_df$Var1, nodes),
  to = match(interaction_df$Var2, nodes) ,
  value = abs(interaction_df$coef_estimates)*5
) %>% 
  mutate(contribution = ifelse(interaction_df$coef_estimates>0, "positive", "negative"))
nods <- data.frame(name=nodes)
graph <- tbl_graph(nodes=nods, edges=edges, directed = F)


# Not specifying the layout - defaults to "auto"

p<-ggraph(graph, layout = 'stress') + 
  geom_edge_link(aes(colour=contribution)) +
  geom_node_point(size=7, color="blue", alpha=0.6)+
  geom_node_text(aes(label = name), vjust = 1.5, size=5.5)+
  theme_graph(base_size = 18)+
  theme(legend.position = "top")
p

# Save the graph 
ggsave("output/interaction_network_yield.png", p, units = "in",
       width = 18, height = 8, dpi = 300)


```

### Nitrogen

```{r}
nitrogen_data <- model_data %>% 
  filter(Trait=="Nitrogen") %>% 
  select(-Trait)
```
#### Definition of the intercept
Let set the intercept to be Crop = cereal, UAV Type = AscTec Pelican, Sensor = Micasense RedEdge, Band = B_G_R_RE_NIR, Algorithm = MLR, and Altitude = 15:
```{r}
# Relevel categorical variables
nitrogen_data$Crop <- relevel(nitrogen_data$Crop, ref = "cereal")
nitrogen_data$Crop <- droplevels(nitrogen_data$Crop) # drop levels that doesn't exist
nitrogen_data$UAV_Type <- relevel(nitrogen_data$UAV_Type, ref = "eBee wing-fixed")
nitrogen_data$UAV_Type <- droplevels(nitrogen_data$UAV_Type)
nitrogen_data$Sensor <- relevel(nitrogen_data$Sensor, ref = "Micasense RedEdge")
nitrogen_data$Sensor <- droplevels(nitrogen_data$Sensor)
nitrogen_data$Band <- relevel(nitrogen_data$Band, ref = "B_G_R_RE_NIR")
nitrogen_data$Band <- droplevels(nitrogen_data$Band)
nitrogen_data$Algorithm <- relevel(nitrogen_data$Algorithm, ref = "MLR")
nitrogen_data$Algorithm <- droplevels(nitrogen_data$Algorithm)

# Set altitude to 15 as a reference: subtract 15 from all the values in the Altitude column. This will make 15 the reference point (i.e., the value where Altitude = 0 in the model).
#nitrogen_data$Altitude_m <- nitrogen_data$Altitude_m
```

#### Preprocess the data
```{r}
nitrogen_data_final <- check_corr(nitrogen_data)
```

#### Model Building


```{r}
library(glmnet)

# Prepare the data
y <- nitrogen_data_final$RPD
X <- select(nitrogen_data_final, -c(RPD))  #-c(RPD, Altitude_m)
X <- as.matrix(X)
X_interactions <- model.matrix(~ (.)^2, data = as.data.frame(X))
X_interactions <- X_interactions[,-1] # remove intercept


# Perform cross-validation to find the best alpha and lambda
set.seed(123)  # For reproducibility
cv_elastic_net <- cv.glmnet(X_interactions, y, alpha = 0.5)  # alpha = 0.5 for Elastic Net

# Extract the best lambda value
best_lambda <- cv_elastic_net$lambda.min

# Fit the final Elastic Net model
final_model <- glmnet(X_interactions, y, alpha = 0.5, lambda = best_lambda)

# View the coefficients
#print(coef(final_model))
```

#### Plot interactions
```{r fig.height=8, fig.width=18, warning=FALSE, fig.dpi=300}
library(networkD3)
library(ggraph)
library(tidygraph)
library(tidyr)
library(dplyr)
set_graph_style(plot_margin = margin(1,1,1,1))

# Get the coefficients of the variables
coefficients <- coef(final_model)
df_coefs <- data.frame(
     variables = names(coefficients[,1]),
     coef_estimates = as.numeric(coefficients[,1])
 )

# Remove zero coefficients
df_coefs <- df_coefs %>% filter(coef_estimates !=0)


# Split variables string in 2 columns using the ':' as the separator
df_coefs2 <- df_coefs %>%
  separate(variables, into = c("Var1", "Var2"), sep = ":")  # Separate the interaction terms

write.csv(df_coefs2, file="output/nitrogen_elasticnet_results.csv", row.names = F)

interaction_df <-df_coefs2 %>% filter(!is.na(Var2))

nodes <- unique(c(interaction_df$Var1, interaction_df$Var2))
edges <- data.frame(
  from = match(interaction_df$Var1, nodes),
  to = match(interaction_df$Var2, nodes) ,
  value = abs(interaction_df$coef_estimates)*5
) %>% 
  mutate(contribution = ifelse(interaction_df$coef_estimates>0, "positive", "negative"))
nods <- data.frame(name=nodes)
graph <- tbl_graph(nodes=nods, edges=edges, directed = F)


# Not specifying the layout - defaults to "auto"

p<-ggraph(graph, layout = 'stress') + 
  geom_edge_link(aes(colour=contribution)) +
  geom_node_point(size=7, color="blue", alpha=0.6)+
  geom_node_text(aes(label = name), vjust = 1.5, size=5.5)+
  theme_graph(base_size = 18)+
  theme(legend.position = "top")
p

# Save the graph 
ggsave("output/interaction_network_nitrogen.png", p, units = "in",
       width = 15, height = 8, dpi = 300)


```










