---
title: "Analysis"
author: "Adama NDOUR"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load package
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(paletteer)
library(meta) # meta-analysis
library(nnet) # Multinomial logit model
library(GGally) # plot model coefficients
library(recipes)
library(recipeselectors)
library(embed) # encoding
library(report) # report statistical results
library(stargazer) # formatting statistical results
library(kableExtra) # format table
library(DHARMa) # plot residuals of a linear model
```


## Load the data
```{r}
df <- read_excel("uav_review_data.xlsx")
```

## Overview of the data
```{r}
#str(df)
```

## Data manipulation: create a model class variable
```{r}
df <- df %>% mutate(
  Model_Class = case_when(
    RPD < 1.4 ~ "unrealiable models",
    RPD >= 1.4 & RPD < 2 ~ "reasonable models",
    RPD >=2 ~ "excellent models"
  )
)

# Remove special characters
df$Sensor <- str_replace_all(df$Sensor, "\r", " ")
df$Sensor <- str_replace_all(df$Sensor, "\n", " ")
df$Sensor <- str_replace_all(df$Sensor, "\\s+", " ")
```

## Exploratory Data Analysis (EDA)

### Typology of Algorithms
```{r}
library(treemap)
library(ggplotify)
algos <- t %>% mutate(tot = sum(n)) %>% mutate(perc = (n/tot)*100)
algos$label <- paste0(algos$n, " %")
algos$label_comp <- paste(algos$Algorithm, algos$label, sep = "\n")
# Open a PNG device
png("output/treemap_algos_2.png", width = 8, height = 6, units = "in",res = 300)
treemap(
  algos,
  index = "Algorithm",
  vSize = "perc",
  title = "",
  fontsize.labels = 12,
  #fontcolor.labels = "white",
)
dev.off()
```

### Which UAV platform maximize the performance of ML models
```{r fig.height=5, fig.width=7, message=FALSE, warning=FALSE, dpi=300}
df_trait <- df %>% filter(Problem=="trait estimation")
#df_trait %>% group_by(Crop,Algorithm)
n_shape_var <- length(unique(df_trait$Sensor))
p<-df_trait %>% 
  group_by(DOI, Trait, UAV_Type, Sensor, Algorithm,Model_Class) %>% 
  summarise(RPD=mean(RPD)) %>% 
  ggplot(aes(y=Algorithm, x=RPD, color=UAV_Type)) +
  geom_point(aes(shape=Sensor))+
  scale_shape_manual(values = 0:n_shape_var) +
  scale_color_paletteer_d("ggthemes::calc")+
  facet_grid(Trait~ Model_Class, scales = "free_y")+
  theme_bw()+
  theme(
    legend.text = element_text(size = 8.5)
  )
ggsave("output/figure1.png",plot = p,dpi = 300)
p
```


### Forest plot for the biomass

```{r fig.height=5, fig.width=10, message=FALSE, warning=FALSE, dpi=300}
# Install and load necessary packages
# Load necessary libraries

# Example RPD data
biomass_data <- df_trait %>% filter(Trait=="AGB")

# Calculate summary statistics
biomass_rpd_summary <- biomass_data %>%
  group_by(Algorithm) %>%
  summarize(
    mean_RPD = mean(RPD),
    sd_RPD = sd(RPD),
    n = n(),
    SEM_RPD = sd_RPD / sqrt(n),
    CI_Lower = mean_RPD - 1.96 * SEM_RPD,
    CI_Upper = mean_RPD + 1.96 * SEM_RPD
  )

# Print the summary
print(biomass_rpd_summary)

# Combine data for all models
biomass_meta_combined <- metagen(
  TE = biomass_rpd_summary$mean_RPD,
  lower = biomass_rpd_summary$CI_Lower,
  upper = biomass_rpd_summary$CI_Upper,
  studlab = biomass_rpd_summary$Algorithm,
  sm = "Mean"
)

# Forest plot for all models
# png(file = "output/forestplot_biomass.png", width = 10, height = 5, res = 300, units = "in")
forest(biomass_meta_combined,
       main = "Forest Plot of RPD for All Models of Biomass Estimation",
       xlab = "RPD",
       label.left = "Models",
       studlab = biomass_rpd_summary$Algorithm,
       print.tau2 = FALSE,
       col.diamond = "blue",
       col.predict = "red",
       leftlabs = c("Models", "Mean", "SE(Mean)"))

```


### Forest plot for the yield

```{r fig.height=5, fig.width=10, message=FALSE, warning=FALSE, dpi=300}
# Install and load necessary packages
# Load necessary libraries

# Example RPD data
yield_data <- df_trait %>% filter(Trait=="Yield")

# Calculate summary statistics
yield_rpd_summary <- yield_data %>%
  group_by(Algorithm) %>%
  summarize(
    mean_RPD = mean(RPD),
    sd_RPD = sd(RPD),
    n = n(),
    SEM_RPD = sd_RPD / sqrt(n),
    CI_Lower = mean_RPD - 1.96 * SEM_RPD,
    CI_Upper = mean_RPD + 1.96 * SEM_RPD
  )

# Print the summary
print(yield_rpd_summary)

# Combine data for all models
yield_meta_combined <- metagen(
  TE = yield_rpd_summary$mean_RPD,
  lower = yield_rpd_summary$CI_Lower,
  upper = yield_rpd_summary$CI_Upper,
  studlab = yield_rpd_summary$Algorithm,
  sm = "Mean"
)

# Forest plot for all models
# png(file = "output/forestplot_yield.png", width = 10, height = 5, res = 300, units = "in")
forest(yield_meta_combined,
       main = "Forest Plot of RPD for All Models for Yield Estimation",
       xlab = "RPD",
       label.left = "Models",
       studlab = yield_rpd_summary$Algorithm,
       print.tau2 = FALSE,
       col.diamond = "blue",
       col.predict = "red",
       leftlabs = c("Models", "Mean", "SE(Mean)"))

```

### Forest plot for the nitrogen

```{r fig.height=5, fig.width=10, message=FALSE, warning=FALSE, dpi=300}
# Install and load necessary packages
# Load necessary libraries
library(meta)

# Example RPD data
nitrogen_data <- df_trait %>% filter(Trait=="Nitrogen")

# Calculate summary statistics
nitrogen_rpd_summary <- nitrogen_data %>%
  group_by(Algorithm) %>%
  summarize(
    mean_RPD = mean(RPD),
    sd_RPD = sd(RPD),
    n = n(),
    SEM_RPD = sd_RPD / sqrt(n),
    CI_Lower = mean_RPD - 1.96 * SEM_RPD,
    CI_Upper = mean_RPD + 1.96 * SEM_RPD
  )

# Print the summary
print(nitrogen_rpd_summary)

# Combine data for all models
nitrogen_meta_combined <- metagen(
  TE = nitrogen_rpd_summary$mean_RPD,
  lower = nitrogen_rpd_summary$CI_Lower,
  upper = nitrogen_rpd_summary$CI_Upper,
  studlab = nitrogen_rpd_summary$Algorithm,
  sm = "Mean"
)

# Forest plot for all models
#png(file = "output/forestplot_nitrogen.png", width = 10, height = 5, res = 300, units = "in")
forest(nitrogen_meta_combined,
       main = "Forest Plot of RPD for All Models of nitrogen Estimation",
       xlab = "RPD",
       label.left = "Models",
       studlab = nitrogen_rpd_summary$Algorithm,
       print.tau2 = FALSE,
       comb.random = FALSE,
       col.diamond = "blue",
       col.predict = "red",
       leftlabs = c("Models", "Mean", "SE(Mean)"))

```

## Multivariate Linear Regression: Key drivers of ML model performance 
```{r}
# Recode RPD variable to convert to factor predictors
df_trait_model <- df_trait %>% 
  mutate(
    RPD_rec = recode_factor(Model_Class, 
                            "unrealiable models" = "Bad",
                            "reasonable models" = "Reliable",
                            "excellent models" = "Excellent"),
    Crop = as_factor(Crop),
    Stage = as_factor(Stage),
    Trait = as_factor(Trait),
    UAV_Type = as_factor(UAV_Type),
    Sensor = as_factor(Sensor),
    Band = as_factor(Band),
    Algorithm = as_factor(Algorithm)
  )
df_trait_model <- df_trait_model %>% 
  select(RPD, Crop, Stage, Trait, UAV_Type, Sensor, Band, Altitude_m, Algorithm)

```


```{r}
# Drop Na
df_trait_model <- df_trait_model %>% drop_na(UAV_Type)
```


### Biomass

```{r}
# Example data
biomass_model_data <- df_trait_model %>% filter(Trait=="AGB")

# Remove trait
biomass_model_data <- biomass_model_data %>% select(-Trait)

# Standardize predictor variables
recipe <- recipe(RPD ~ ., data=biomass_model_data) %>%
    # convert string to factor
    #step_string2factor(all_nominal()) %>%
    # remove no variance predictors 
    #recipes::step_nzv(all_nominal()) %>%
    # factor to  dummy variables
    #step_dummy(all_nominal(), one_hot=T) %>%
    step_lencode_mixed(all_nominal_predictors() , outcome=vars(RPD)) %>%
    # remove non-variance variables
    step_nzv(where(is.numeric)) %>%
    #step_dummy(all_nominal_predictors(), one_hot=F) %>%  # Convert categorical   variables to dummy variables
    prep()

# juice recipe
biomass_model_data_final <- juice(recipe)

# Fit the multinomial logistic regression model
biomass_model <- lm(RPD ~. , data = biomass_model_data)
```


### Yield

```{r}
# Example data
yield_model_data <- df_trait_model %>% filter(Trait=="Yield")

# Remove trait
yield_model_data <- yield_model_data %>% select(-Trait)

# Standardize predictor variables
recipe <- recipe(RPD ~ ., data=yield_model_data) %>%
    # convert string to factor
    #step_string2factor(all_nominal()) %>%
    # remove no variance predictors 
    #recipes::step_nzv(all_nominal()) %>%
    # factor to  dummy variables
    #step_dummy(all_nominal(), one_hot=T) %>%
    step_lencode_mixed(all_nominal_predictors() , outcome=vars(RPD)) %>%
    # remove non-variance variables
    step_nzv(where(is.numeric)) %>%
    #step_dummy(all_nominal_predictors(), one_hot=F) %>%  # Convert categorical   variables to dummy variables
    prep()

# juice recipe
yield_model_data_final <- juice(recipe)

# Fit the multinomial logistic regression model
yield_model <- lm(RPD ~. , data = yield_model_data)
```

### Nitrogen

```{r}
# Example data
nitrogen_model_data <- df_trait_model %>% filter(Trait=="Nitrogen")

# Remove trait
nitrogen_model_data <- nitrogen_model_data %>% select(-Trait)

# Standardize predictor variables
recipe <- recipe(RPD ~ ., data=nitrogen_model_data) %>%
    # convert string to factor
    #step_string2factor(all_nominal()) %>%
    # remove no variance predictors 
    #recipes::step_nzv(all_nominal()) %>%
    # factor to  dummy variables
    #step_dummy(all_nominal(), one_hot=T) %>%
    step_lencode_mixed(all_nominal_predictors() , outcome=vars(RPD)) %>%
    # remove non-variance variables
    step_nzv(where(is.numeric)) %>%
    #step_dummy(all_nominal_predictors(), one_hot=F) %>%  # Convert categorical   variables to dummy variables
    prep()

# juice recipe
nitrogen_model_data_final <- juice(recipe)

# Fit the multinomial logistic regression model
nitrogen_model <- lm(RPD ~. , data = nitrogen_model_data)
```

## Report results
### Biomass
* Model
```{r message=FALSE, warning=FALSE}
report_model(biomass_model)
```

* Performance
```{r message=FALSE, warning=FALSE}
report_performance(biomass_model)
```

* Parameters
```{r message=FALSE, warning=FALSE}
report_parameters(biomass_model)
```
 * Summary
```{r}
library(flextable)
library(officer)
#stargazer(biomass_model, type = "text")
#sjPlot::tab_model(biomass_model, show.p = T, show.ci = T)
# Create a summary of the model
biomass_model_summary <- summary(biomass_model)

# Extract coefficients
biomass_coefficients <- as.data.frame(biomass_model_summary$coefficients)

# Create a beautiful table

# Create a flextable object
# ft <- flextable(biomass_coefficients)
# 
# # Customize the flextable
# ft <- theme_vanilla(ft)
# ft <- autofit(ft)
# ft <- set_caption(ft, caption = "Customized Sample Table")
# 
# # Additional styling
# ft <- bold(ft, part = "header")
# ft <- bg(ft, part = "header", bg = "lightblue")
# ft <- color(ft, part = "header", color = "white")
# ft <- border_remove(ft)
# ft <- border_outer(ft, border = fp_border(color = "black", width = 1))
# ft <- border_inner_h(ft, border = fp_border(color = "gray", width = 0.5))
# ft <- border_inner_v(ft, border = fp_border(color = "gray", width = 0.5))
# 
# # Display the flextable
# ft
# Create beautiful table
kable(biomass_coefficients, format = "simple")  
```
 
### Yield
* Model
```{r message=FALSE, warning=FALSE}
report_model(yield_model)
```

* Performance
```{r message=FALSE, warning=FALSE}
report_performance(yield_model)
```

* Parameters
```{r message=FALSE, warning=FALSE}
report_parameters(yield_model)
```
 * Summary
```{r message=FALSE, warning=FALSE}
#stargazer(yield_model, type = "text")
#sjPlot::tab_model(yield_model, show.p = T, show.ci = T)
# Create a summary of the model
yield_model_summary <- summary(yield_model)

# Extract coefficients
yield_coefficients <- as.data.frame(yield_model_summary$coefficients)

# Create a beautiful table
kable(yield_coefficients, format = "simple")  
```

### Nitrogen
* Model
```{r message=FALSE, warning=FALSE}
report_model(nitrogen_model)
```

* Performance
```{r message=FALSE, warning=FALSE}
report_performance(nitrogen_model)
```

* Parameters
```{r message=FALSE, warning=FALSE}
report_parameters(nitrogen_model)
```
 * Summary
```{r message=FALSE, warning=FALSE}
#stargazer(nitrogen_model, type = "text")
#sjPlot::tab_model(nitrogen_model, show.p = T, show.ci = T)
# Create a summary of the model
nitrogen_model_summary <- summary(nitrogen_model)

# Extract coefficients
nitrogen_coefficients <- as.data.frame(nitrogen_model_summary$coefficients)

# Create a beautiful table
kable(nitrogen_coefficients, format = "simple") 
```

## Plot the residuals
### Biomass
```{r message=FALSE, warning=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE, dpi=300}
biomass_simulationOutput <- simulateResiduals(fittedModel = biomass_model)
plot(biomass_simulationOutput)
```

### Yield
```{r message=FALSE, warning=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE, dpi=300}
yield_simulationOutput <- simulateResiduals(fittedModel = yield_model)
plot(yield_simulationOutput)
```


### Nitrogen
```{r message=FALSE, warning=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE, dpi=300}
nitrogen_simulationOutput <- simulateResiduals(fittedModel = nitrogen_model)
plot(nitrogen_simulationOutput)
```


